Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-04-05 paper/main.tex
Add wing frames image and edit introduction to include it

Forces produced by the flapping wings of insects, birds and micro air vehicles
are of crucial importance for flight, yet they are subtle and difficult to
model.  Many studies have developed equations and solution techniques to
understand the fluid flow around these wings, to compute control actions
required for stable flight, or to optimize wing design. Aerodynamic studies
related to insect flight and intermediate Reynolds numbers (Re 100-10,000) have
generally focused on either numerical solutions of Navier-Stokes equations in
two or three dimensions \cite{wu2004unsteady,wang2000two}, quasi-steady
approximations of the observed behavior
\cite{sane2002aerodynamic,ellington1984aerodynamics}, or a comparison of both
methods \cite{pesavento2004falling}.  The Navier-Stokes equations offer
important insights into the full character of the fluid around the wing
including vorticity and fluid-structure interaction, but are complex and
computationally expensive to calculate.  Quasi-steady approximations, in
contrast, capture most of the character of the aerodynamic forces without any
detailed modeling of the fluid flow.  These equations are phenomenological in
nature and constitute an assembly of terms that are consistent with aerodynamic
theory that can be used to represent lift, drag and other forces, as functions
of a wing's kinematic variables such as velocity and angle of attack.  Both
methods have shown qualitative and quantitative agreement with experiments
\cite{wang2004unsteady}.

@@

>>>>

Forces produced by the flapping wings of insects, birds and micro air vehicles
are of crucial importance for flight, yet they are subtle and difficult to
model. In many cases, the flapping motion is only partially actuated and
controlled, while essential characteristics like angle of attack through the
wing stroke result passively from complex inertial and aerodynamic forces and
rely on the compliance of a flexible wing structure.
Figure~\ref{fig:wing_frames} shows a sequence of frames from a high-speed video
of a flexible 3D printed wing being actuated only in the primary flapping
motion, yet the wing passively twists and deflects to achieve an angle of attack
of approximately 45\textdegree, which allows it to produce vertical lift.

Many studies have developed equations and solution techniques to
understand the fluid flow around flapping wings, to compute control actions
required for stable flight, or to optimize wing design. Aerodynamic studies
related to insect flight and intermediate Reynolds numbers (Re 100-10,000) have
generally focused on either numerical solutions of Navier-Stokes equations in
two or three dimensions \cite{wu2004unsteady,wang2000two}, quasi-steady
approximations of the observed behavior
\cite{sane2002aerodynamic,ellington1984aerodynamics}, or a comparison of both
methods \cite{pesavento2004falling}.  The Navier-Stokes equations offer
important insights into the full character of the fluid around the wing
including vorticity and fluid-structure interaction, but are complex and
computationally expensive to calculate.  Quasi-steady approximations, in
contrast, capture most of the character of the aerodynamic forces without any
detailed modeling of the fluid flow.  These equations are phenomenological in
nature and constitute an assembly of terms that are consistent with aerodynamic
theory that can be used to represent lift, drag and other forces, as functions
of a wing's kinematic variables such as velocity and angle of attack.  Both
methods have shown qualitative and quantitative agreement with experiments
\cite{wang2004unsteady}.

@@

\begin{figure}
\centering
\includegraphics[trim=0 120 70 170, clip, width=0.8\textwidth]{figures/wing_frames}
\caption{Composite image showing the flapping motion of a 3D printed
  wing captured in high-speed video.\label{fig:wing_frames}}
\end{figure}
